\fontfamily{phv}\selectfont{Research A Proposal}

### 2013-09-24 docs/proposal/doc.tex
voortgang in stukje over connectivity

\subsection*{Brain connectivity}
\subsubsection*{Functional connectivity}
Functional
%The Functional connectivity is defined as the temporal dependence of neuronal activity patterns of anatomically separated brain regions \cite{friston1993functional}.
%An increasing body of studies successfully investigates functional connectivity by applying statistical methods on the level of co-activation of resting-state fMRI time-series between brain regions.
%Several studies have shown that resting-state networks reflect brain connectivity in a concise way, though their exact relation remains unknown \cite{Lowe2000, doria2010, Bullmore2009}.
%Resting state indicating that subjects are instructed to relax without thinking of something in particular, to stimulate spontaneous brain activity.

\subsubsection*{Structural connectivity}
The structural connectivity is a mapping of the physical paths in the brain, and it shows the neural connections between anatomically separated brain regions.
This is strongly related with functional connectivity: regions can only be functionally connected if there is a physical connection between them. \cite{vandenheuvel2009}

>>>>

\subsection*{Brain connectivity}
\subsubsection*{Functional connectivity}
The functional connectivity describes the statistical dependance of neuronal activity of different brain regions \cite{friston1993functional}.
This gives an insight in the organization of the brain, even though the exact functioning is still unclear \cite{Lowe2000, doria2010, Bullmore2009}.
Functional connectivity is strongly time-dependant, as these dependancies may be short-lasting.

%The Functional connectivity is defined as the temporal dependence of neuronal activity patterns of anatomically separated brain regions \cite{friston1993functional}.
%An increasing body of studies successfully investigates functional connectivity by applying statistical methods on the level of co-activation of resting-state fMRI time-series between brain regions.
%Several studies have shown that resting-state networks reflect brain connectivity in a concise way, though their exact relation remains unknown \cite{Lowe2000, doria2010, Bullmore2009}.
%Resting state indicating that subjects are instructed to relax without thinking of something in particular, to stimulate spontaneous brain activity.

\subsubsection*{Structural connectivity}
The structural connectivity is a mapping of the physical paths in the brain, and it shows the neural connections between anatomically separated brain regions.
This is strongly related with functional connectivity: regions can only be functionally connected if there is a physical connection between them.
This is an intuitive relation, and is also shown experimentally \cite{vandenheuvel2009}.
